% Created 2025-05-04 Sun 07:45
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{minted}
\usepackage[margin=1in]{geometry}
\author{Duncan Bennett}
\date{\today}
\title{Development Log}
\hypersetup{
 pdfauthor={Duncan Bennett},
 pdftitle={Development Log},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.1 (Org mode 9.5.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

This document contains notes, todos, references and resources used in the
development of this repo. It should be in the .gitignore file.

\section*{XGBoost}
\label{sec:orgbea5820}
\url{https://xgboost.readthedocs.io/en/latest/python/sklearn\_estimator.html}
\section*{PCA Preprocessing}
\label{sec:org44b1785}
\href{https://safjan.com/before-pca/}{Reference}
\begin{itemize}
\item handle missing values
\begin{itemize}
\item remove variable if too many missing values
\item replace NaN with mean/median (or some other technique) if a good
proportion of data is there
\item Standardize to mean 0, variance 1
\item Apply PCA and take most of the variance
\end{itemize}
\end{itemize}
\section*{\textit{<2025-04-28 Mon> } Some reference papers}
\label{sec:orgffa50cd}
\begin{itemize}
\item \href{https://www.matec-conferences.org/articles/matecconf/pdf/2020/05/matecconf\_cscns2020\_05009.pdf}{PCA + ARIMA}
\item \href{https://nixustechnologies.com/anomaly-detection-with-arima-model-using-python/}{Anomoly detection with ARIMA}
\end{itemize}
\section*{{\bfseries\sffamily TODO} \textit{<2025-04-25 Fri>}Learn AWS}
\label{sec:orgdd5ada6}
Learn AWS to be able to run this code on a virtual machine/cloud instance
and, in particular, use a GPU to train the model. This will be especially
useful when using ViT and Transformers in general.
\subsection*{{\bfseries\sffamily DONE} \textit{<2025-04-25 Fri>}Sign up for AWS}
\label{sec:org5120248}
\subsection*{{\bfseries\sffamily TODO} \textit{<2025-04-25 Fri>}Test run a machine}
\label{sec:org3c22179}
Outline the process for cloning, downloading data and running python code
on a machine. Possible automate this into one script.


\section*{{\bfseries\sffamily TODO} \textit{<2025-04-25 Fri> } EDA with credit card fraud data}
\label{sec:org4c8308d}
\begin{itemize}
\item class imbalance
\item naive dimension reduction?
\item missing data
\item how to handle missing data form "identity.csv"?
\end{itemize}
\end{document}